\documentclass[11pt]{article}
% \usepackage{times}
\usepackage{palatino}
\usepackage{colortbl}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\renewcommand{\baselinestretch}{1.2} 
\setlength{\topmargin}{-1.0in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\textheight}{10.1in}

\newlength{\pagewidth}
\setlength{\pagewidth}{6.5in}
\pagestyle{empty}

\def\pp{\par\noindent}

\special{papersize=8.5in,11in}


\begin{document}
\noindent 
Tony Li \\
CSE150 \\
HW04 \\\\

%==============================================Problem 1===================================================
\noindent\textbf{\underline{Problem 1}}\\

I have twelve books.

	\begin{itemize}
		\item In how many ways can I line them up on a single shelf?

		12! = \textbf{479,001,600}

		\item In how many ways can I choose seven of them and line them up on a single shelf?
		
		$\frac{12!}{5!}$ = \textbf{3,991,680}

		\item In how many ways can I choose seven to take to school?

		${12 \choose 7}$ = $\frac{12!}{7!5!}$ = \textbf{792}
	\end{itemize}

%==============================================Problem 2===================================================
\noindent\textbf{\underline{Problem 2}}\\

An ogre has $n$ captives to eat, one captive per day.

	\begin{enumerate}
		\item How many ways are there to make a menu for $n$ days?

		\textbf{n!}

		\item How many ways are there to pick $k$ captives to freeze them for winter season?

		${n \choose k}$ = $\frac{n!}{k!(n-k)!}$

		\item How many ways are there to buy $n$ bottles of sauce for the captives, out of $k$ kinds?

		${k \choose n}$ = $\frac{k!}{n!(k-n)!}$
	\end{enumerate}

%==============================================Problem 3===================================================
\noindent\textbf{\underline{Problem 3}}\\

	\begin{itemize}
		\item An ice-cream vendor sells eleven kinds of ice-cream. In how many different ways can I buy 
		six cones, some or even all of which could be the same.

		

		\item An icecream vendor sells six kinds of ice-cream. In how many different ways can I buy
		eleven cones, some or even all of which could be the same.

		
	\end{itemize}













\end{document}